DeepSphere: a graph-based spherical CNN

### 2019-11-15 main.tex
move big figure and remove newpage
comment todos for submission

\begin{description}
	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
\end{description}

story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
\begin{itemize}
	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
\end{itemize}

contributions:
\begin{itemize}
	\item theory $\Rightarrow$ convergence (better graph)
	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
	\item surprising: anisotropy doesn't seem useful
\end{itemize}

\todo{
TODO:
\begin{itemize}
	\item Unify vocabulary and avoid synonyms.
		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
		Signal, maps, fields, functions.
		Irregular, uneven, non-uniform.
		Coarsening, down-sampling.
		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
	\item check English vs American English
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer commenter
	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
	\item Show the three samplings in a figure?
	\item better abstract (Friday's talk abstract?)
	\item conclusion: less speculation?
	\item check feedback from ICLR'20 LTS2 reading group
	\item \mdeff{check my Telegram notes}
	\item argue against more generality
	\item figure that show the three samplings? (suggested by reviewer \#2)
\end{itemize}
}

\todo{
last pass:
\begin{itemize}
	\item figure placement
	\item check footnotes
\end{itemize}
}

\todo{
Not done:
\begin{itemize}
	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel). \nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore. It's quite minor.}
	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
	\item Add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?} \mdeff{They don't write how their Laplacian was built. Also, they only did MNIST on the sphere...}
\end{itemize}
}

\clearpage
\newpage

@@

@@

\begin{figure}
	\begin{minipage}{0.6\linewidth}
		\centering
		\includegraphics[width=\linewidth]{equivariance_error}
		\caption{
			Mean equivariance error \eqref{eq:mean equivariance error}.
			There is a clear tradeoff between equivariance and computational cost, governed by the number of vertices $n$ and edges $kn$.
		}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
% \vspace{-0.5cm}
\end{figure}

@@

\newpage
\subsubsection*{Author Contributions}
Left blank for anonymity reason.
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

>>>>

%\begin{description}
%	\item[git] \url{https://github.com/nperraud/deepsphere_v2_paper}
%	\item[overleaf] \url{https://www.overleaf.com/project/5d31d2fbd6859d54cb707212}
%	\item[openreview] \url{https://openreview.net/forum?id=B1e3OlStPB}
%\end{description}
%
%story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
%\begin{itemize}
%	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
%	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
%\end{itemize}
%
%contributions:
%\begin{itemize}
%	\item theory $\Rightarrow$ convergence (better graph)
%	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
%	\item surprising: anisotropy doesn't seem useful
%\end{itemize}
%
%\todo{
%TODO:
%\begin{itemize}
%	\item Unify vocabulary and avoid synonyms.
%		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
%		Signal, maps, fields, functions.
%		Irregular, uneven, non-uniform.
%		Coarsening, down-sampling.
%		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
%	\item check English vs American English
%	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
%	\item update pygsp and merge sphere branch
%	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
%	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
%	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
%\end{itemize}
%}
%
%\todo{
%rebuttal:
%\begin{itemize}
%    \item answer commenter
%	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
%	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
%	\item Show the three samplings in a figure?
%	\item better abstract (Friday's talk abstract?)
%	\item conclusion: less speculation?
%	\item check feedback from ICLR'20 LTS2 reading group
%	\item \mdeff{check my Telegram notes}
%	\item argue against more generality
%	\item figure that show the three samplings? (suggested by reviewer \#2)
%\end{itemize}
%}
%
%\todo{
%last pass:
%\begin{itemize}
%	\item figure placement
%	\item check footnotes
%\end{itemize}
%}
%
%\todo{
%Not done:
%\begin{itemize}
%	\item Do the experiments on the icosahedral sampling with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel). \nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore. It's quite minor.}
%	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
%	\item Add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?} \mdeff{They don't write how their Laplacian was built. Also, they only did MNIST on the sphere...}
%\end{itemize}
%}
%
%\clearpage
%\newpage

@@

\begin{figure}
	\begin{minipage}{0.6\linewidth}
		\centering
		\includegraphics[width=\linewidth]{equivariance_error}
		\caption{
			Mean equivariance error \eqref{eq:mean equivariance error}.
			There is a clear tradeoff between equivariance and computational cost, governed by the number of vertices $n$ and edges $kn$.
		}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}

@@

@@

\subsubsection*{Author Contributions}
Left blank for anonymity reason.
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.
